### 2021-05-10 content/31.tooling-table.tex
Fixed table
Added SCHEMA and LifeMonitor and RO-Crate DMP to table

\begin{table}[ht]
	\centering
	\begin{tabular}{llll}
		\toprule
		\textbf{Tool name} & Targets & Language / Platform & Status \\
		\multicolumn{4}{l}{\it Brief Description} \\
		\midrule

@@

@@

		\textbf{galaxy2cwl} \citep{galaxy2cwl} & Workflow developers & Python & Alpha \\
		\multicolumn{4}{l}{\it Wraps Galaxy workflow as Workflow RO-Crate} \\
		\bottomrule
	\end{tabular}
	\caption{Applications and libraries implementing RO-Crate, targeting different types of users across multiple programming languages. Status is indicative as assessed by this work.}
	\label{tab:tools}
\end{table}

>>>>

\begin{table}[htbp]
	\centering
	\begin{tabular}{llll}
		\toprule
		\textbf{Tool name} & Targets & Language / Platform & Status \\
		\multicolumn{4}{l}{\it Brief Description} \\
		\midrule

@@

		\textbf{Life Monitor} \citep{about-lifemonitor} & Workflow developers & Python & Beta \\
		\multicolumn{4}{l}{\it Workflow testing and monitoring service; Workflow Testing profile of RO-Crate} \\

        \textbf{SCHeMa} & Workflow users & PHP & Alpha \\
        \multicolumn{4}{l}{\it Workflow execution using RO-Crate as exchange mechanism } \\

		\textbf{galaxy2cwl} \citep{galaxy2cwl} & Workflow developers & Python & Alpha \\
		\multicolumn{4}{l}{\it Wraps Galaxy workflow as Workflow RO-Crate} \\

@@

        \textbf{Ro-Crate\_2\_ma-DMP} \citep{doi:10.5281/zenodo.3903463} & Data Management Plan users & Python & Beta \\
        \multicolumn{4}{l}{\it Convert between machine-actionable data management plans (maDMP) and RO-Crate \citep{doi:10.4126/frl01-006423291} }

		\bottomrule
	\end{tabular}
	\caption{Applications and libraries implementing RO-Crate, targeting different types of users across multiple programming languages. Status is indicative as assessed by this work.}
	\label{tab:tools}
\end{table}
